A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
applicability, is now outcome determinicity

We now describe our {\em switching} planning system that operates
according to the continual planning paradigm, given a description of
the current problem and domain in DTPDDL. The system {\em
switches}, in the sense that planning proceeds in interleaved
sessions, in which the base planner is either {\em sequential}/linear
or {\em decision-theoretic}.
%%
During a sequential session, a rewarding {\em trace} of a possible
execution is computed using a cost-optimising satisficing planner
which trades action costs, goal rewards, and determinacy.
%%
Formatted as a linear plan, the trace specifies a sequence of actions
that achieves some reachable goals following a deterministic
approximation of the problem at hand.
%%
Structurally, a trace is a sequence of elements that are either: (i) ground
actions from the DTPDDL description of the world, or (ii) atomic {\em
assumptions}, modelled as deterministic actions, made about the truth
value of facts that can only be determined at runtime (e.g., that a
box of cornflakes is located on the corner bench in the kitchen).
%%
The system always begins in a sequential session, so that plan
execution proceeds by applying DTPDDL actions from the trace in
sequence until the applicability of the next scheduled action is too
uncertain according to a threshold parameter~(here, 95\%). In that
eventuality a DT session commences, which tailors sensory processing
to determine whether the assumptions made in the trace hold, or which
otherwise acts to achieve the goals.

Because online DT planning in large problems is impractical (we seek
response times in seconds), DT sessions plan in an abstract process
determined by the current trace and underlying belief-state. This
abstraction is constructed by first excluding all propositions (and
related actions) that are not true, or {\em assumed } true, of states
in the trace, then adding them back, using as an heuristic the entropy
of the trace assumptions conditional on a candidate
proposition. Propositions are added, one at a time, until the number
of states in the initial belief-state reaches a given
threshold.\footnote{Our experiments are performed using a number of
different threshold parameters.}  To the resulting abstract model we
also add {\em disconfirm} and {\em confirm} actions that the
DT session can schedule in order to judge an atomic assumption
in the trace. In the abstract model these actions yield a relatively
small reward if the corresponding judgement is true (or small penalty
otherwise). If a judgement action is scheduled for execution the
DT session is terminated, and control is returned to a
sequential session.

>>>>

We now describe our {\em switching} planning system that operates
according to the continual planning paradigm, given a description of
the current problem and domain in DTPDDL. The system {\em
switches}, in the sense that planning proceeds in interleaved
sessions, in which the base planner is either {\em sequential}/linear
or {\em decision-theoretic}.
%%
During a sequential session, a rewarding {\em trace} of a possible
execution is computed using a cost-optimising satisficing planner
which trades action costs, goal rewards, and determinacy.
%%
Formatted as a linear plan, the trace specifies a sequence of actions
that achieves some reachable goals following a deterministic
approximation of the problem at hand.
%%
Structurally, a trace is a sequence of elements that are either: (i) ground
actions from the DTPDDL description of the world, or (ii) atomic {\em
assumptions}, modelled as deterministic actions, made about the truth
value of facts that can only be determined at runtime (e.g., that a
box of cornflakes is located on the corner bench in the kitchen).
%%
The system always begins in a sequential session, so that plan
execution proceeds by applying DTPDDL actions from the trace in
sequence until the outcome of executing the next scheduled action is
too uncertain according to a threshold parameter~(here, 95\%). In that
eventuality a DT session commences, which tailors sensory processing
to determine whether the assumptions made in the trace hold, or which
otherwise acts to achieve the goals.

Because online DT planning in large problems is impractical (we seek
response times in seconds), a DT session plans in an abstract process
determined by the current trace and underlying belief-state. This
abstraction is constructed by first excluding all propositions (and
related actions) that are not true, or {\em assumed } true, of states
in the trace, then adding them back, using as an heuristic the entropy
of the trace assumptions conditional on a candidate
proposition. Propositions are added, one at a time, until the number
of states in the initial belief-state reaches a given
threshold.\footnote{Our experiments are performed using a number of
different threshold parameters.}  To the resulting abstract model we
also add {\em disconfirm} and {\em confirm} actions that the
DT session can schedule in order to judge an atomic assumption
in the trace. In the abstract model these actions yield a relatively
small reward if the corresponding judgement is true (or small penalty
otherwise). If a judgement action is scheduled for execution the
DT session is terminated, and control is returned to a
sequential session.
